FinalManuscript_DISCS_UG

### 2018-06-23 parts/01_introduction_00.tex
Tentative context and objectives

In this section of the paper, you want to provide the general background and motivation of your study. This can be done defining some key definitions or ideas that govern your study, presenting your context, and narrowing it down with parameters that shall concretize your study. 
This chapter is divided into four parts: the Context of the Study, the Research Objective/s, the Research Questions, the Scope and Limitations, and finally, the Significance of the Study. Each will be described in greater detail in their respective sections. Appendix A summarizes major points for each of these sections and gives sample guide questions for your reference.

\input{parts/01_introduction_01contextofstudy}
\input{parts/01_introduction_02researchquestions.tex}
\input{parts/01_introduction_03objectives.tex}
\input{parts/01_introduction_05scopeandlimitations}
\input{parts/01_introduction_04significanceofstudy}

>>>>

\input{parts/01_introduction_01contextofstudy}
\input{parts/01_introduction_03objectives.tex}
\input{parts/01_introduction_02researchquestions.tex}
\input{parts/01_introduction_05scopeandlimitations}
\input{parts/01_introduction_04significanceofstudy}

### 2018-06-23 parts/01_introduction_01contextofstudy.tex
Tentative context and objectives

Data privacy and security is a growing concern in various fields \textbf{[insert fields here]}. To meet these needs, cryptography is often employed to secure data. Cryptographic encryption schemes allow data to be transmitted over a insecure channel, and thus much research has been done on the development and application of various encryption schemes.

\textbf{[insert examples here]}. \textbf{[insert examples here]}.

However, recently, in addition to the secure transmission of data, there is also interest in the secure modification of data. \textbf{insert examples here}.

To allow for operations on encrypted data while maintaining data secrecy, homomorphic encryption schemes have been developed.

>>>>

Digital data privacy and security is a growing concern in various fields, such as  \textbf{[insert fields here]}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys. a cryptosystem also has an encryption algorithm, which maps a plaintext to a ciphertext, and a decryption algorithm, which maps a ciphertext to a plaintext, given an appropiate key \cite[p.119]{tilborg_encyclopedia_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over a insecure channel:  and thus much research has been done on the development and application of various cryptosystems.

One such particular application of cryptography is image encryption. \cite{arul_murugan_survey_2018}

\textbf{[discuss image encryption briefly, note how main concern is security]}

However, research has also considered a type of cryptosystem, homomorphic cryptosystems, where in addition to allowing the secure transmission of data, it is also possible to perform computations with encrypted data. \cite{fontaine_survey_2007}.

### 2018-06-23 parts/01_introduction_03objectives.tex
Tentative context and objectives

\section{Research Objectives}
With your context established, it is in this section where you will now describe what you intend to achieve by the end of the study. A possible way of presenting this subsection is to first introduce what problem/s you wish to address given the current context, and based on that/these, you present the objectives that would somehow address that/these problem/s. Other common things discussed may include a brief overview of your intended methodology.

\begin{enumerate}
    \item Research objectives 1...
    \item Research objectives 2...
    \item Research objectives 3...
\end{enumerate}

>>>>

\section{Research Objectives}
Our study aims to provide an objective comparision of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.
In this study, we wish to
\begin{enumerate}
    \item Compare the applicability of known homorphic encryption schemes to common image processsing operations, in other words, determine which schemes permit the most operations;
		\item Compare the security of common image processsing operations under known homorphic encryption schemes, using established statistical methods in image encryption;
    \item Compare the efficiency of common image processsing operations under known homorphic encryption schemes;
    \item Create a plug-in for the Open Source Computer Vision Library (OpenCV) to allow for convenient use of homomorphic encryption schemes.
\end{enumerate}
